### 2021-07-05 README.Rmd
use GH actions

[![rOpenSci Badge](https://badges.ropensci.org/87_status.svg)](https://github.com/ropensci/onboarding/issues/87)[![JOSS status](http://joss.theoj.org/papers/c85f57adbc565b064fb4bfc9b59a1b2a/status.svg)](http://joss.theoj.org/papers/c85f57adbc565b064fb4bfc9b59a1b2a)[![DOI](https://zenodo.org/badge/50553382.svg)](https://zenodo.org/badge/latestdoi/50553382)[![Travis Build Status](https://travis-ci.org/ropensci/visdat.svg?branch=master)](https://travis-ci.org/ropensci/visdat)[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ropensci/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/ropensci/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/ropensci/visdat/master.svg)](https://codecov.io/github/ropensci/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](http://cran.rstudio.com/web/packages/visdat/index.html)[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

>>>>

<!-- badges: start -->
[![rOpenSci Badge](https://badges.ropensci.org/87_status.svg)](https://github.com/ropensci/onboarding/issues/87)[![JOSS status](http://joss.theoj.org/papers/c85f57adbc565b064fb4bfc9b59a1b2a/status.svg)](http://joss.theoj.org/papers/c85f57adbc565b064fb4bfc9b59a1b2a)[![DOI](https://zenodo.org/badge/50553382.svg)](https://zenodo.org/badge/latestdoi/50553382)[![R-CMD-check](https://github.com/ropensci/visdat/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/visdat/actions)[![Codecov test coverage](https://codecov.io/gh/ropensci/visdat/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](http://cran.rstudio.com/web/packages/visdat/index.html)[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges: end -->
